\documentclass[../../main.tex]{subfiles}
\begin{document}
%
    First and foremost, I would like to to express my gratitude to Nuno Araújo for giving me the opportunity to work at CFTC and introducing me to this fascinating topic. It has been a pleasure to work here under his guidance, where his mentoring and hard work have helped me become a better scientist.
    
    I would like to express my deepest gratitude to Pedro Patrício for all he taught me, the advice, and most importantly, the time and patience spent with me on my work. Without him, I feel, this work would be lacking. 
    
    I would like to extend my thanks to the people from CFTC that were always reachable and prompt to help, and from whom I learnt a lot. A special thanks to Didier for all the discussions and camaraderie.
    
    Finally, a special thanks to my family and friends for the continuous support throughout the years.

\begin{comment}
I would like to thank Nuno Araujo first and foremost, for his wise mentoring, inexhaustible energy, and ´
unwavering patience. I am truly grateful for the opportunities he has given me.
I would like to thank Cristovao Dias, who has greatly helped me in many ways when producing this ˜
work, including supplying part of the code used in chapter 4. I would like to mention my office mates,
Andre Matias and Luıs Rebelo, who have provided fruitful discussions and camaraderie, as well as all
of CFTC, particularly Margarida Telo da Gama, Mykola Tasinkevych, Andre Nunes and Diogo Pinto. ´
Cell-mediated self-assembly is but a small fraction of the knowledge I have acquired from all of these
people.
Lastly, I would like to thank my parents and my friends, without which I would not be able to finish nor
start this endeavor.
%
%
%
%
%
I would like to thank Nuno Araujo, for introducing me to the topic of soft-matter physics, in particular ´
the topic of granular matter, and also for his hard work, astonishing persistence and for providing me the
opportunity to grow as a physicist.
I would like to thank Troy Shinbrot for guiding me during my stay in Princeton and Rutgers University. I also thank Sundar Sundaresan and Jari Kolehmainen for helpful discussions.
I would also like to thank Goncalo Antunes, Luıs Rebelo, Cristovao Dias, Andre Nunes and Diogo
Pinto for their helpful input. The last thank is towards my family, in particular my parents and my brother
for the continuous support and the occasional simple, but challenging, question.
I would like to acknowledge the financial support from the Luso-American Development Foundation
(FLAD), FLAD/NSF, Proj. 273/2016
%
%
%
%
%
First of all, my gratitude goes to Professor Jon Shah for giving me the opportunity to work at the Institute
of Neurosciences and Medicine of the Forschungszentrum Jülich in INM-4. It was a privilege to work
there. I am thankful to be part of such important research group and to experience a real research environment. The funding received from the student program for the last six months of the internship was
essential for this project.
In addition, I would like to thank Doctor Yun Seong Dae for giving me the opportunity to work with him
in this project. I am grateful for all he taught me, for all the given advice, time and patience spent on my
work.
I would also like to express my gratitude to Liliana Caldeira who welcomed me in the Institute and not
only guided me through my stay, but also eased my arrival.
Furthermore, Professor Nuno Matela also has my gratitude, since it was him who first introduced me
to this fascinating topic and prestigious institute. Although not a constant presence due to the existent
distance, he was always reachable and prompt to help, support and provide feedback whenever required.
He was someone who helped me path my future and I hope I can always count on his guidance.
I would like to thank the staff of the Institute of Neurosciences and Medicine of the Forschungszentrum
Jülich for providing me with the conditions to learn more about neurosciences and for all their sympathy
and encouragement during my stay. A special thanks to INM-4 and MR/PET physics group for all your
support and interesting discussions.
I would like to express my deepest gratitude to the Professors of the Institute of Biophysics and Biomedical Engineering for all the time, sympathy, encouragement and knowledge during the last five years.
Once again, the funding I received from the Erasmus Program was essential for this project.
This work was only possible with the support of my family. A special thanks to my parents, grandparents, uncles and aunt for their moral support and encouragement, not only during this work but also
throughout my academic path. Without their help, I would not have been able to neither start nor finish this journey.
Finally, a warm thank you from the bottom of my heart to both my old and new friends. I am grateful
to those who encouraged me while I left to another country and welcomed me again as I returned. I am
grateful to those I met in this journey, as they made my stay abroad much more exciting and blissful. A
kind word to my flatmate and friend. It was a year really full of colour.
%
%
%
%
%
Agradeço à minha família (meu pai, minha mãe, minha mulher, meus três filhos, meu
irmão e restante família) e a todos quantos nas últimas quase três décadas, partilharam
bons e maus momentos e bons e maus resultados, em toda a minha vida não só familiar,
mas acima de tudo, académica e profissional e também em toda a minha vida pública,
enquanto servidor da coisa pública e protagonista da vida política, quer ao nível
autárquico e parlamentar e também ao nível governativo.
Agradeço, sobretudo aqueles, que se mantiveram fieis inabalavelmente à lealdade,
competência, diligencia, sacrifício, honradez, sinceridade, amizade e confidencia.
\end{comment}

%
\end{document}